\documentclass[10pt]{article}

% Packages
\usepackage[margin=0.5in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}

% Define colors
\definecolor{darkblue}{RGB}{0, 25, 51}

% Formatting for section titles
\titleformat{\section}{\large\bfseries\color{darkblue}}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{5pt}

% Remove default paragraph indentation
\setlength{\parindent}{0pt}

% Custom command for job entries
\newcommand{\jobtitle}[4]{
    \textbf{#1} \textbar\ \textit{#2} \textbar\ #3 \hfill \textbf{#4}
}

% Custom command for job descriptions
\newcommand{\jobdesc}[1]{
    \begin{itemize}[nosep, leftmargin=0.25in]
        #1
    \end{itemize}
}

% Remove page numbers
\pagestyle{empty}

% Start document
\begin{document}

% Header
\begin{center}
    \textbf{\Large Dennis Gavrilenko} \\
    (925) 470-7127 \textbar\ \href{mailto:dennisg009@gmail.com}{dennisg009@gmail.com} \textbar\ \href{http://www.linkedin.com/in/dennis-gavrilenko}{linkedin.com/in/dennis-gavrilenko} \textbar\ \href{http://www.interosity.co}{interosity.co}
\end{center}

% Education Section
\section{EDUCATION}

\textbf{University of California, Los Angeles (UCLA)} \textbar\ Los Angeles, CA \hfill \textbf{Sep 2021 -- Mar 2025} \\
B.A. in Business Economics, Minor in Data Science Engineering \textbar\ GPA: 3.7/4.0, Dean's Honor List \textbar\ SAT: 1580, ACT: 35 \\
\textit{Relevant Coursework: Natural Language Processing, Computer Vision, Data Science, Intro to ML, Econometrics, \\ Programming in R, Intro to Computer Science I/II, Linear Algebra, Probability Theory, Calculus I/II/III, Intro Accounting}

\vspace{5pt}

\textbf{Sciences Po} \textbar\ Paris, France \hfill \textbf{Aug 2023 -- Dec 2023} \\
\textit{Semester Exchange: International Trade \& Finance, Labor Economics, Corporate Governance, French Imperial History}

% Professional Experience Section
\section{PROFESSIONAL EXPERIENCE}

\jobtitle{UCLA Undergraduate Admission}{Campus Tour Guide}{Los Angeles, CA}{Jan 2023 -- Mar 2025}
\jobdesc{
    \item Provided in-depth, informative, 90-minute tours of the UCLA campus to 2000+ guests (prospective/admitted students).
    \item Showed everyone how wonderful and amazing UCLA is and encouraged thousands of students to pursue higher education.
}

\vspace{3pt}

\jobtitle{Boston Consulting Group (BCG)}{Summer Associate}{Seattle, WA}{Jun 2024 -- Aug 2024}
\jobdesc{
    \item Recommended strategies for a major US family foundation's board to reduce staff tensions and streamline operations.
    \item Interviewed 20+ executives, board members, industry leaders to identify best operations practices to address pain points.
    \item Led an extensive analysis of 40+ major US cities to identify the best location for an upcoming headquarters move.
    \item Conducted a peer benchmarking analysis to identify client's weak points in OpEx, grantmaking efficiency, and impact.
}

\vspace{3pt}

\jobtitle{The Kraft Heinz Company}{Product Manager Intern}{Chicago, IL}{Jun 2023 -- Aug 2023}
\jobdesc{
    \item Helped build four data-driven dashboards for digital supply chain team while managing 15+ stakeholder interests.
    \item Created an interactive visualization model with Excel pivot tables, decreasing unordered customer inventory by 20\%.
    \item Coordinated product development with 10+ data engineers and UX designers to align product vision with business goals.
}

\vspace{3pt}

\jobtitle{Amazon Prime Gaming}{Product Consultant}{Los Angeles, CA}{Apr 2023 -- Jun 2023}
\jobdesc{
    \item Developed a product roadmap and designed 5+ high-fidelity mock-ups in Figma for Amazon Prime Gaming's website.
    \item Created two strategies to gamify UX with weekly website prizes, increasing user retention by 25\% and signups by 10\%.
}

\vspace{3pt}

\jobtitle{kommu}{Product Manager Intern}{Los Angeles, CA}{Mar 2023 -- Jun 2023}
\jobdesc{
    \item Planned technical feature set and designed 20+ high-fidelity mock-ups in Figma for a startup's new web portal login.
    \item Analyzed 200+ users' data to determine top growing markets, recommended three new marketing strategies for Q3, Q4.
}

\vspace{3pt}

\jobtitle{Hussle}{Marketing Lead}{Los Angeles, CA}{Aug 2022 -- Dec 2022}
\jobdesc{
    \item Collaborated with development and customer success teams to create two new app features based on user feedback.
    \item Directed all marketing operations, created \$3000 marketing budget, distributed 1000+ flyers, organized 3 outreach efforts.
}

\vspace{3pt}

\jobtitle{First Republic Bank}{Lending Services Intern}{San Francisco, CA}{Jun 2022 -- Sep 2022}
\jobdesc{
    \item Digitized paper housing records system to simplify documentation access and increase loan closing team's efficiency.
    \item Built Excel dashboard with pivot tables and VBA to analyze 100+ intern surveys, recommended 3 areas for improvement.
    \item Continuously communicated, implemented changing needs for 40+ stakeholders, including 2 managers and 35+ clients.
}

% Leadership and Volunteer Section
\section{LEADERSHIP AND VOLUNTEER EXPERIENCE}

\jobtitle{The Bruin Group Consulting}{Project Manager, Senior Consultant}{Los Angeles, CA}{Jan 2022 -- Mar 2025}
\jobdesc{
    \item Led a 10-week, 5-person project to create growth strategies to increase a startup carpooling service's user base by 300\%.
    \item Created a developer marketing strategy and implementation timeline for a startup's SaaS and API products.
}

\vspace{3pt}

\jobtitle{Boy Scouts of America}{Senior Patrol Leader, Quartermaster}{Antioch, CA}{Feb 2014 -- Sep 2021}
\jobdesc{
    \item Led my troop of 20+ Scouts on extended camping trips, earned 51 merit badges, advanced 10+ younger Scouts' ranks.
    \item Participated in several city clean-ups, Christmas tree pickups while volunteering hundreds of community service hours.
    \item Volunteered in 13 Eagle Scout Projects, earned 2 Eagle Scout Mentor pins, National Youth Leadership Training.
}

% Skills Section
\section{SKILLS AND INTERESTS}

\textbf{Programming Skills:} Data Analysis (Python, R, SQL, VBA, Excel, PowerPoint), Project Management (Jira, Notion, Agile Development, Scrum), Product Marketing (User Research, A/B Testing, Setting KPIs), Java, C++.

\vspace{3pt}

\textbf{Languages:} Fluent in English and Russian, learning French so that I can talk to the Parisian baker in my neighborhood.

\vspace{3pt}

\textbf{Achievements:} Backpacked the Pacific Crest Trail (2025), Eagle Scout, LA Marathon finisher (2023, 2024), SF Marathon finisher (2024), climbed highest volcano in CA (Mt. Shasta) twice, curated art gallery in LA, WayUp Top 100 Intern (2023).

\vspace{3pt}

\textbf{Interests:} Growing ghost peppers, reading science fiction novels, juggling, poker, geology, raising chickens, postcards, \\ Roman archaeology, playing the accordion, long-distance cycling, blogging on Substack, Blokus, hitchhiking, regular hiking.

\end{document}